---
title: "Coding Assignment 2"
author: "Team 5"
date: "Due: 2022-10-23 23:59"
output:
  html_document:
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
#Put any packages you need here
knitr::opts_chunk$set(echo = TRUE)
```

A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r dataset, include=FALSE}
insurance <- read.csv("../Data/insurance_0026_Group5.csv")
```



## Question 1

Generate this regression equation:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children + \beta_{4}*Female + \beta_{5}*Smoker + \beta_{6}*WinterSprings + \beta_{7}*WinterPark + \beta_{8}*Oviedo$$

```{r q1}
model <- lm(Charges~ Age + BMI + Female + Children + Smoker +WinterSprings + WinterPark + Oviedo, data = insurance)
summary(model)

```
Charges = -13802.87 + 300Age + 258.88BMI + 1671.80Female + 621.73Children + 25963.57Smoker -486.51WinterSprings + 450.98WinterPark - 543.85Oviedo 

Which independent variables test significant in a two-tailed test? Use $\alpha = 0.2$

Age, BMI, and Smoker test significant in a two-tailed test.

## Question 2

Interpret the coefficients of all the independent variables that tested significant.

In the case of a 80% confidence level (alpha = 0.2 from above):

If someones age goes up by 1 year, the charge goes up $300.97 give or take $89.82.
If someones BMI goes up by 1 percent, the charge goes up $258.88 give or take $219.77.
If someone is a smoker, the charge goes up by $25,963.57 give or take $2,863.41.

## Question 3

The insurance agent returns with another client:

- Age: 35
- BMI: 26
- Children: 1
- Gender: Female
- Smoker: No
- City: Sanford

Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)

```{r q3}
newPrediction <- data.frame(Age = 35,
                            BMI = 26,
                            Children = 1,
                            Female = 1,
                            Smoker = 0,
                            WinterSprings = 0,
                            WinterPark = 0,
                            Oviedo = 0)

predict(model, newdata = newPrediction,
        interval = 'confidence')

```
Medical expenses would be between $77.54 and $11,433.53 with a fit of $5,755.53.

## Question 4

Compare the model from question 1, to a model that does not include the group of city dummies. Does including the cities reduce the SSE by a statistically significant amount? (check the partial F-test for significance of the dummies as a group). Use $\alpha = 0.05$

```{r q4}

dataminuscities <- insurance[,c('Charges','Age','BMI','Female','Children','Smoker')]

model2 <- lm(Charges~ Age + BMI + Female + Children + Smoker, data = dataminuscities) 
summary(model2)

anova(model2, model)
```
Including the cities did not reduce the sum of squared errors by a significant amount due to P (0.9779) > alpha (0.05), meaning that adding the city variables did not really reduce the difference between the observed medical expenses and the predicted medical expenses. 



